To Airbnb?: Factors impacting short-term leasing preference

### 2018-11-10 papers/round_2_reviews.Rmd
Finalize reviewer response

### What's Changed

@@

@@

### Direct responses to reviewers

@@

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE}

  library(ggplot2)

   load(file.path('c:/code', 'research', 'airbnbMelbourne',
                  'data', 'analyzed', 'reviewers.RData'))

  imp_df$bed_lab <- paste0(imp_df$bedrooms, ' Beds')
  fig_cap <- paste0('This figure compares the estimated long term rent for short term rental properties via the hedonic\n imputation method (X-axis) and the matched pairs-type method (Y-axis).  It is broken down by\n structure type (Apartment vs House) and by bedroom count.')

  ggplot(imp_df,
         aes(x=ltr_imp_revenueH, y=ltr_imp_revenueK, col = type)) + 
    geom_point(alpha = .5, size=.5) + 
    facet_grid(type ~ bed_lab) + 
    xlab('\nHedonic Revenue\n') + 
    ylab('Matched Pairs Revenue (A$)\n') + 
    theme(legend.position = 'none',
          plot.caption=element_text(hjust = 0.3),
          plot.title = element_text(hjust = 0.5)) +
    scale_color_manual(values = c('red', 'blue')) + 
    scale_x_continuous(breaks = c(15000, 30000, 45000),
                       labels = c('$15k', '$30k', '$45k'))+
    scale_y_continuous(breaks = c(15000, 30000, 45000),
                       labels = c('$15k', '$30k', '$45k'))+
    geom_abline(intercept = 0, slope = 1, linetype = 2,
                color = 'gray50') +
    labs(caption = fig_cap,
         title = 'Comparison of Hedonic and Matched Pairs Imputation')

```

>>>>

## What's Changed

@@

6. Shortened data preparation section

@@

## Direct responses to reviewers

@@
